Software Citation Principles

### 2016-03-07 sc-principles/software-citation-principles.tex
added author names to ref in Table 1 caption
capitalized FORCE11 on first page

\rowcolors{2}{white}{gray!25}
\begin{table}[htbp]
\caption{Varieties of software mentions in publications, from  \cite{howison2015jasist}} 
\centering
\scriptsize\setlength{\tabcolsep}{2.5pt}
\begin{tabular}{@{}l l l } % p{0.6\textwidth}@{}}
\toprule
Mention Type & \multicolumn{2}{c}{Count (n=286)} \\ % & Example \\
\midrule
Cite to publication & 105 & 37\% \\ %& \ldots was calculated using biosys (Swofford \& Selander 1981). \newline Ref: Swofford DL, Selander RB (1981) biosys-1: a Fortran program for the comprehensive analyses of electrophoretic data in population genetics and systematics. \emph{Journal of Heredity}, 72, 281–283.\\
Cite to users manual & 6 & 2\% \\ %& \ldots as analyzed by the BIAevaluation software (Biacore, 1997). \newline Ref: Biacore, I. (1997). BIAevaluation Software Handbook, version 3.0 (Uppsala, Sweden: Biacore, Inc) \\
Cite to name or website & 15 & 5\% \\ %& \ldots using the program Autodecay version 4.0.29 PPC (Eriksson 1998). \newline Ref: ERIKSSON, T. 1998. Autodecay, vers. 4.0.29 Stockholm:Department of Botany. \\
Instrument-like & 53 & 19\% \\ %& \ldots calculated by t-test using the Prism 3.0 software (GraphPad Software, San Diego, CA, USA). \\
URL in text & 13 & 5\% \\ %& \ldots freely available from http://www.cibiv.at/software/pda/. \\
In-text name only & 90 & 31\% \\ %& \ldots were analyzed using MapQTL (4.0) software. \\
Not even name & 4 & 1\% \\ %& \ldots was carried out using software implemented in the Java programming language. \\
\bottomrule
\end{tabular}
\label{tab:mentions}
\end{table}%

The Force11 Software Citation Working Group~\cite{f11scwg} was created in April 2015, with the following mission statement:

>>>>

\rowcolors{2}{white}{gray!25}
\begin{table}[htbp]
\caption{Varieties of software mentions in publications, from Howison and Bullard~\cite{howison2015jasist}.} 
\centering
\scriptsize\setlength{\tabcolsep}{2.5pt}
\begin{tabular}{@{}l l l } % p{0.6\textwidth}@{}}
\toprule
Mention Type & \multicolumn{2}{c}{Count (n=286)} \\ % & Example \\
\midrule
Cite to publication & 105 & 37\% \\ %& \ldots was calculated using biosys (Swofford \& Selander 1981). \newline Ref: Swofford DL, Selander RB (1981) biosys-1: a Fortran program for the comprehensive analyses of electrophoretic data in population genetics and systematics. \emph{Journal of Heredity}, 72, 281–283.\\
Cite to users manual & 6 & 2\% \\ %& \ldots as analyzed by the BIAevaluation software (Biacore, 1997). \newline Ref: Biacore, I. (1997). BIAevaluation Software Handbook, version 3.0 (Uppsala, Sweden: Biacore, Inc) \\
Cite to name or website & 15 & 5\% \\ %& \ldots using the program Autodecay version 4.0.29 PPC (Eriksson 1998). \newline Ref: ERIKSSON, T. 1998. Autodecay, vers. 4.0.29 Stockholm:Department of Botany. \\
Instrument-like & 53 & 19\% \\ %& \ldots calculated by t-test using the Prism 3.0 software (GraphPad Software, San Diego, CA, USA). \\
URL in text & 13 & 5\% \\ %& \ldots freely available from http://www.cibiv.at/software/pda/. \\
In-text name only & 90 & 31\% \\ %& \ldots were analyzed using MapQTL (4.0) software. \\
Not even name & 4 & 1\% \\ %& \ldots was carried out using software implemented in the Java programming language. \\
\bottomrule
\end{tabular}
\label{tab:mentions}
\end{table}%

The FORCE11 Software Citation Working Group~\cite{f11scwg} was created in April 2015, with the following mission statement:
